### 2022-03-08 paper/output/document/thesis_4_applications.tex
my back hurts

Because these common sense facts can determine my system's judgements, they are part of the trusted
code base for my system, or the logic and code that a user must trust in order to trust my system. 
Changing these common sense facts will change the judgements 
that my system makes. For example, if we define truth telling as an act that is self-contradictory (perhaps
by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
Malicious common sense facts and definitions will result in bad ethical judgements. 
The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
system, and virtually all prior attempts in machine ethics face similar challenges.\footnote{See Section
Related Work for a survey of the common sense required in prior work.} Many prior attempts
sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.

This chapter will provide examples of the kinds of common sense facts required to get my system
off the ground. I use a lean and uncontroversial common sense database
to achieve robust and powerful results. This serves as evidence for the ease of automating
Kantian ethics, an example of the additional work required to use my system in practice, and a 
demonstration of my system's power and flexibility. These examples demonstrate that, armed with nuanced 
common sense facts, my system can make sophisticated judgements faithful to philosophical literature.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lies and Jokes \label{joking}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The moral status of lying is hotly debated in the Kantian literature. I focus on two dilemmas
presented in Korsgaard's ``Right to Lie," which 
examines how strict Kant's prohibition on lying is \citep{KorsgaardRTL}. She begins with the case of 
lying and joking. Many of Kant's critics argue that his prohibition on lies includes lies told in 
the context of a joke, which should be permissible. Korsgaard responds by arguing 
that there is a crucial difference between lying and joking: lies involve deception, but jokes do not. 
The purpose of a joke is amusement, which does not rely on the listener believing the story told. 
Given appropriate definitions of lies and jokes, my system shows that jokes are permissible but lies 
are not, demonstrating its power and flexibility. This section demonstrates how my system can be used 
in practice; it needs to be given some baseline common sense facts, but with those facts, it can make 
sophisticated judgements. Moreover, because my system is faithful to definitions found in philosophical 
literature, it can perform nuanced reasoning, demonstrating the value of faithful automated ethics.

First, Korsgaard argues that the categorical imperative prohibits lies because they involve deception. 
When universalized, lies will no longer be believed, so lying could never be an effective way of achieving 
any goal when universalized. Korsgaard points out that ``we believe what is said to us in a given 
context because most of the time people in that context say what they really think'' \citep[4]{KorsgaardRTL}. 
In order to formalize this argument, I first need to define the relevant terms and assumptions, which include
lying and Korsgaard's argument about the basis of trust.

I define lying and trust in terms of belief. As in Section \ref{details}, I choose thin, or minimal,
definitions of terms like belief to reduce the potential for controversy in my system's factual background.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ believe{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\ believes\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
%
\isamarkupcmt{\texttt{believe} is a constant that maps a subject and a term to another DDL term. For example, 
subject ``Sara'' might believe the term ``the sky is blue'' to create the sentence ``Sara believes
that the sky is blue,'' which can be true or false at a world.%
}%
\begin{isamarkuptext}%
Logicians and epistemologists develop and debate complex logics of belief and knowledge \citep{seplogicbelief}. 
I avoid this complexity by defining the concept of belief simply as a constant that maps a subject, term pair 
to a term. For the examples in this section, this choice suffices. 
I encode some minimal properties of belief below, but avoid any full definition of the term.

@@

lying are prohibited. First, I define the subject and maxim at hand.%

@@

of lying and relatively uncontroversial facts about the world. The logical background needed is the fact that lying
requires knowingly uttering a falsehood with the goal that someone believe the falsehood, a definition
of lying that is relatively well-accepted. The factual background needed consists of the fact that if 

@@

There are two implications of this section. First, my system is capable of performing ethical reasoning
sophisticated enough to show that lying is prohibited but joking is not. This is a direct consequence 
of my system's use of a robust conception of a maxim, which encodes the goal of an act as part of the 
maxim being evaluated. Because my implementation is faithful to philosophical literature, it is able 
to recreate Korsgaard's solution to a complex ethical dilemma that philosophers debated for decades. Second, 
in the process of making this argument precise, my system isolated a necessary and sufficient condition 
of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
the falsehood. This condition both made an long-standing argument in Kantian ethics more precise
and can guide the correct formulation of future maxims. In other words, an insight generated by the 
computer provides value to ethicists, bolstering the argument for computational ethics provided in 
Section Computational Ethics.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lying to a Liar \label{murderer}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
My system can not only distinguish between lying and joking, but it can also resolve the paradox of 
the murderer at the door. In this dilemma, murderer Bill knocks on your door asking about Sara, his 
intended victim. Sara is at home, but moral intuition says that you should lie to Bill and say 
that she is out to prevent him from murdering her. Many critics of Kantian ethics argue that the 
FUL prohibits you from lying in this instance; if everyone lied to murderers, then murderers wouldn't 
believe the lies and would search the house anyways. Korsgaard resolved this centuries-long debate by 
noting that the maxim of lying to a murderer is actually that of lying to a liar: Bill cannot 
announce his intentions to murder; instead, he must ``must suppose that you do not know who he is 
and what he has in mind'' \citep{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will 
lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5 
of \citep{KorsgaardRTL}, she accepts that her arguments will not apply in the case of the honest murderer 
who announces his intentions, so she restricts her focus to the case of lying to a liar. She claims 
that in the case of the honest murderer, the correct act is to refuse to respond.} Thus, the maxim 
in question specifies that when someone lies to you, you are allowed to lie to them. The maxim of 
lying to the murderer is actually the maxim of lying to a liar, which is permissible.

In this section, I formalize her argument for the permissibility of lying to a liar. First, I define

@@

\isamarkupcmt{This example involves one additional subject: the murderer.%

@@

\isamarkupcmt{This is one of two assumptions that encode Korsgaard's core argument. If person1 believes that person2 
utters a sentence as a falsehood, then person1 won't believe that sentence. This is a modification of the 

@@

saying a false sentence, then I won't believe that sentence.%

@@

@@

\isamarkupcmt{This is the second major common sense assumption. If the maxim (c, a, g) is universalized, then 
if person1 believes that person2 believes they are in the given circumstances, then person1 believes 
that person2 performs the act. In other words, person1 will believe that 
person2 wills the maxim. I will refer to this as the ``convention of willing'' assumption. This follows

@@

wills it and thus notices the pattern of everyone willing it. If you observe that many do X in circumstances C,
you will assume that everyone does X in circumstance C.%

@@

and of ordinary definitions of lying. These thin assumptions were sufficient to generate moral conclusions
that Kantian scholars debate robustly. Armed with this common sense, my system generated 

@@

While this example demonstrates the power of my system, it
also shows how vital the role of the common sense reasoning is. Slight, intuitive changes in the factual
background achieved completely different conclusions about lying. This example also demonstrates the importance
and difficulty of correctly formulating the maxim, particularly its circumstances.
Korsgaard's argument for the permissibility of lying to a 
murderer hinged on a clever formulation of the maxim that highlights the fact that the murderer is lying to you.
The need for common sense reasoning to evaluate the universalizability test and to formulate a maxim
is a potential limitation of my system, and I adress this concern in Section \ref{whatisamaxim} and 
Section Limitations.

@@

these kinds of judgements demonstrate that, with additional work, my system could be used in pratice 
to guide AI agents. A ``smart doorbell'' like those created by Ring may face a dilemma like that of 
the murderer at the door. Such a doorbell equipped with a more application-ready version of my 

@@

%:%135=91%:%
%:%136=92%:%
%:%137=93%:%
%:%138=94%:%
%:%139=95%:%
%:%140=96%:%
%:%141=97%:%
%:%143=100%:%
%:%144=100%:%
%:%146=101%:%
%:%147=102%:%
%:%148=102%:%
%:%149=103%:%
%:%150=103%:%
%:%151=104%:%
%:%153=105%:%
%:%154=105%:%
%:%155=106%:%
%:%156=106%:%
%:%157=107%:%
%:%159=108%:%
%:%160=109%:%
%:%161=110%:%
%:%162=111%:%
%:%163=112%:%
%:%166=116%:%
%:%167=117%:%
%:%168=118%:%
%:%169=119%:%
%:%170=120%:%
%:%171=121%:%
%:%172=122%:%
%:%173=123%:%
%:%174=124%:%
%:%175=125%:%
%:%177=127%:%
%:%178=127%:%
%:%179=128%:%
%:%181=129%:%
%:%184=131%:%
%:%185=132%:%
%:%186=133%:%
%:%187=134%:%
%:%188=135%:%
%:%189=136%:%
%:%190=137%:%
%:%191=138%:%
%:%192=139%:%
%:%193=140%:%
%:%194=141%:%
%:%195=142%:%
%:%196=143%:%
%:%198=145%:%
%:%199=145%:%
%:%201=146%:%
%:%202=147%:%
%:%203=148%:%
%:%204=148%:%
%:%205=149%:%
%:%206=149%:%
%:%208=150%:%
%:%209=151%:%
%:%210=151%:%
%:%211=152%:%
%:%212=152%:%
%:%214=153%:%
%:%217=155%:%
%:%218=156%:%
%:%219=157%:%
%:%220=158%:%
%:%222=160%:%
%:%223=160%:%
%:%224=161%:%
%:%225=162%:%
%:%227=163%:%
%:%228=163%:%
%:%229=164%:%
%:%231=165%:%
%:%232=166%:%
%:%233=166%:%
%:%234=167%:%
%:%236=168%:%
%:%237=169%:%
%:%238=170%:%
%:%239=171%:%
%:%240=172%:%
%:%241=173%:%
%:%242=173%:%
%:%243=174%:%
%:%245=175%:%
%:%246=175%:%
%:%247=176%:%
%:%254=177%:%
%:%255=177%:%
%:%256=178%:%
%:%257=178%:%
%:%258=179%:%
%:%259=179%:%
%:%261=180%:%
%:%262=181%:%
%:%263=182%:%
%:%264=183%:%
%:%265=183%:%
%:%266=184%:%
%:%267=184%:%
%:%268=185%:%
%:%269=185%:%
%:%270=186%:%
%:%271=186%:%
%:%272=187%:%
%:%273=187%:%
%:%274=187%:%
%:%276=188%:%
%:%277=189%:%
%:%278=189%:%
%:%279=190%:%
%:%289=192%:%
%:%290=193%:%
%:%291=194%:%
%:%292=195%:%
%:%293=196%:%
%:%294=197%:%
%:%295=198%:%
%:%296=199%:%
%:%297=200%:%
%:%298=201%:%
%:%299=202%:%
%:%300=203%:%
%:%301=204%:%
%:%302=205%:%
%:%304=207%:%

@@

%:%306=208%:%
%:%308=209%:%
%:%309=210%:%
%:%312=212%:%
%:%313=213%:%
%:%314=214%:%
%:%315=215%:%
%:%316=216%:%
%:%317=217%:%
%:%318=218%:%
%:%319=219%:%
%:%320=220%:%
%:%322=222%:%

@@

%:%324=223%:%
%:%325=224%:%
%:%327=225%:%

@@

%:%329=226%:%
%:%331=227%:%
%:%332=228%:%

@@

%:%334=229%:%
%:%336=230%:%

@@

%:%338=231%:%
%:%340=232%:%

@@

%:%342=233%:%
%:%345=234%:%
%:%349=234%:%

@@

%:%352=235%:%
%:%353=236%:%
%:%354=237%:%
%:%355=238%:%
%:%356=239%:%
%:%366=242%:%
%:%367=243%:%
%:%368=244%:%
%:%369=245%:%
%:%370=246%:%
%:%371=247%:%
%:%372=248%:%
%:%373=249%:%
%:%374=250%:%
%:%375=251%:%
%:%376=252%:%
%:%377=253%:%
%:%378=254%:%
%:%379=255%:%
%:%380=256%:%
%:%381=257%:%
%:%382=258%:%
%:%383=259%:%
%:%384=260%:%
%:%385=261%:%
%:%386=262%:%
%:%387=263%:%
%:%388=264%:%
%:%389=265%:%
%:%390=266%:%
%:%391=267%:%
%:%392=268%:%
%:%393=269%:%
%:%394=270%:%
%:%395=271%:%
%:%396=272%:%
%:%397=273%:%
%:%398=274%:%
%:%399=275%:%
%:%400=276%:%
%:%401=277%:%
%:%402=278%:%
%:%403=279%:%
%:%404=280%:%
%:%405=281%:%
%:%406=282%:%
%:%407=283%:%
%:%408=284%:%
%:%409=285%:%
%:%410=286%:%
%:%419=289%:%
%:%431=292%:%
%:%432=293%:%
%:%433=294%:%
%:%434=295%:%
%:%435=296%:%
%:%436=297%:%
%:%437=298%:%
%:%438=299%:%
%:%439=300%:%
%:%440=301%:%
%:%441=302%:%
%:%442=303%:%
%:%443=304%:%
%:%444=305%:%
%:%445=306%:%
%:%446=307%:%
%:%447=308%:%
%:%448=309%:%
%:%450=311%:%
%:%451=311%:%

@@

%:%454=312%:%

@@

@@

%:%459=315%:%
%:%460=316%:%

@@

@@

%:%466=318%:%

@@

@@

%:%471=320%:%

@@

@@

%:%477=324%:%
%:%480=326%:%
%:%481=327%:%
%:%482=328%:%
%:%483=329%:%
%:%485=331%:%
%:%486=331%:%

@@

%:%489=332%:%

@@

@@

%:%495=335%:%

@@

@@

%:%500=337%:%

@@

@@

%:%506=341%:%
%:%522=373%:%
%:%523=374%:%
%:%524=375%:%
%:%525=376%:%
%:%526=377%:%
%:%527=378%:%
%:%528=379%:%
%:%529=380%:%
%:%530=381%:%
%:%532=383%:%
%:%533=383%:%

@@

%:%535=385%:%

@@

%:%538=386%:%

@@

@@

%:%542=388%:%

@@

@@

%:%546=391%:%
%:%547=392%:%
%:%548=393%:%
%:%549=394%:%

@@

@@

%:%554=397%:%
%:%555=398%:%
%:%556=399%:%
%:%557=400%:%
%:%558=401%:%
%:%559=402%:%

@@

@@

%:%564=405%:%

@@

%:%569=407%:%
%:%573=407%:%
%:%574=407%:%
%:%575=407%:%

@@

%:%578=409%:%
%:%579=410%:%
%:%589=412%:%
%:%590=413%:%
%:%591=414%:%
%:%592=415%:%
%:%594=417%:%
%:%595=417%:%

@@

@@

%:%599=419%:%

@@

@@

%:%603=421%:%

@@

@@

%:%607=423%:%

@@

@@

%:%611=425%:%

@@

@@

%:%615=428%:%

@@

%:%624=430%:%
%:%625=430%:%

@@

%:%630=432%:%

@@

%:%635=434%:%

@@

%:%640=436%:%

@@

%:%651=439%:%
%:%652=440%:%
%:%653=441%:%
%:%654=442%:%
%:%655=443%:%
%:%656=444%:%
%:%657=445%:%
%:%658=446%:%
%:%659=447%:%
%:%660=448%:%
%:%661=449%:%
%:%662=450%:%
%:%663=451%:%
%:%664=452%:%
%:%665=453%:%
%:%666=454%:%
%:%667=455%:%
%:%668=456%:%
%:%669=457%:%
%:%670=458%:%
%:%671=459%:%
%:%672=460%:%
%:%673=461%:%
%:%674=462%:%
%:%675=463%:%
%:%676=464%:%
%:%677=465%:%
%:%678=466%:%
%:%679=467%:%
%:%680=468%:%
%:%681=469%:%
%:%682=470%:%
%:%683=471%:%
%:%684=472%:%
%:%685=473%:%
%:%686=474%:%

>>>>

Because these common sense facts can determine my system's judgements, they are part of the trusted
code base for my system, or the logic and code that a user must trust in order to trust my system. 
Changing these common sense facts will change the judgements 
that my system makes. For example, if we define truth telling as an act that is self-contradictory (perhaps
by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
Malicious common sense facts and definitions will result in bad ethical judgements. 
The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
system, and virtually all prior attempts in machine ethics face similar challenges.\footnote{See Section
\ref{relatedwork} for a survey of the common sense required in prior work.} Many prior attempts
sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.

This chapter will provide examples of the kinds of common sense facts required to get my system
off the ground. I use a lean and uncontroversial common sense database
to achieve robust and powerful results. This serves as evidence for the ease of automating
Kantian ethics, an example of the additional work required to use my system in practice, and a 
demonstration of my system's power and flexibility. These examples demonstrate that, armed with nuanced 
common sense facts, my system can make sophisticated judgements faithful to philosophical literature.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lies and Jokes \label{joking}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The moral status of lying is hotly debated in the Kantian literature. I focus on two dilemmas
presented in Korsgaard's ``Right to Lie,'' which 
examines Kant's prohibition on lying \citep{KorsgaardRTL}. She begins with the case of 
lying and joking. Many of Kant's critics argue that his prohibition on lies includes lies told in 
the context of a joke, which should be permissible. Korsgaard responds by arguing 
that there is a crucial difference between lying and joking: lies involve deception, but jokes do not. 
The purpose of a joke is amusement, which does not rely on the listener believing the story told. 
Given appropriate definitions of lies and jokes, my system shows that jokes are permissible but lies 
are not, demonstrating its power and flexibility. This section demonstrates how my system can be used 
in practice; it needs to be given some baseline common sense facts, but with those facts, it can make 
sophisticated judgements. Moreover, because my system is faithful to definitions found in philosophical 
literature, it can perform nuanced reasoning, demonstrating the value of faithful automated ethics.

First, Korsgaard argues that the categorical imperative prohibits lies because they involve deception. 
When universalized, lies will no longer be believed, so lying could never be an effective way of achieving 
any goal when universalized. Korsgaard points out that ``we believe what is said to us in a given 
context because most of the time people in that context say what they really think'' \citep[4]{KorsgaardRTL}. 
In order to formalize this argument, I first need to define lying and formalize Korsgaard's argument 
about the basis of trust.

I define lying and trust in terms of belief. As in Section \ref{details}, I choose thin, or minimal,
definitions to reduce the potential for controversy in my system's factual background.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ believe{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\ believes\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
%
\isamarkupcmt{\texttt{believe} is a constant that maps a subject and a term to another DDL term. For example, 
subject ``Sara'' might believe the term ``the sky is blue'' to create the sentence ``Sara believes
that the sky is blue,'' which can be true or false at a world.%
}%
\begin{isamarkuptext}%
Logicians and epistemologists develop and debate complex logics of belief and knowledge \citep{seplogicbelief}. 
I avoid this complexity by defining the concept of belief simply as a constant that maps a subject, term pair 
to a term. For the examples in this section, this choice suffices. 
I encode some minimal properties of belief below, but avoid any full definition of the term.

@@

lying are prohibited. First, I define the relevant subject and maxim.%

@@

of lying and relatively uncontroversial facts about the world. My system needs two pieces of common 
sense to complete this proof. First, I defined lying as knowingly uttering a falsehood with the goal 
that someone believe the falsehood, a definition of lying that is relatively well-accepted. Second, I 
assumed (following in Korsgaard's footsteps) that if 

@@

There are two implications of this section. First, my system is capable of performing ethical reasoning
sophisticated enough to show that lying is prohibited but joking is not. This is a direct consequence 
of my system's use of a robust conception of a maxim, which encodes the goal of an act as part of the 
maxim being evaluated. Because my implementation is faithful to philosophical literature, it is able 
to recreate Korsgaard's solution to a complex ethical dilemma that philosophers debated for decades. Second, 
in the process of making this argument precise, my system isolated a necessary and sufficient condition 
of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
the falsehood. This condition both made an long-standing argument in Kantian ethics more precise
and can guide the correct formulation of future maxims. In other words, an insight generated by the 
computer provides value to ethicists, bolstering the argument for computational ethics provided in 
Section \ref{computationalethics}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lying to a Liar \label{murderer}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
My system can not only distinguish between lying and joking, but it can also resolve the paradox of 
the murderer at the door. In this dilemma, murderer Bill knocks on your door asking about Sara, his 
intended victim. Sara is at home, but moral intuition says that you should lie to Bill and say 
that she is out to prevent him from murdering her. Many critics of Kantian ethics argue that the 
FUL prohibits you from lying in this instance; if everyone lied to murderers, then murderers wouldn't 
believe the lies and would search the house anyways. Korsgaard resolved this centuries-long debate by 
noting that the maxim of lying to a murderer is actually that of lying to a liar: Bill cannot 
announce his intentions to murder; instead, he must ``must suppose that you do not know who he is 
and what he has in mind'' \citep{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will 
lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5, 
she accepts that her arguments will not apply in the case of the honest murderer 
who announces his intentions, so she restricts her focus to the case of lying to a liar. She claims 
that in the case of the honest murderer, the correct act is to refuse to respond. Since I am formalizing
Korsgaard's argument, I also accept this assumption.} Thus, the maxim 
in question specifies that when someone lies to you, you are allowed to lie to them. The maxim of 
lying to the murderer is actually the maxim of lying to a liar, which is permissible.

In this section, I formalize Korsgaard's argument for the permissibility of lying to a liar. First, I define

@@

\isamarkupcmt{This example involves the murderer as an additional subject.%

@@

\isamarkupcmt{This is one of two assumptions that encode Korsgaard's core argument. If $p1$ believes that $p2$ 
utters a sentence as a falsehood, then $p1$ won't believe that sentence. This is a modification of the 

@@

lying, then I won't believe you.%

@@

\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}c\ a\ g\ w{\isachardot}\ {\isasymforall}p{\isadigit{1}}{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isasymforall}p{\isadigit{2}}{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}universalized\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isacharparenleft}p{\isadigit{1}}\ believes\ {\isacharparenleft}p{\isadigit{2}}\ believes\ c{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}p{\isadigit{1}}\ believes\ {\isacharparenleft}a\ p{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline

@@

\isamarkupcmt{This is the second major common sense assumption. If the maxim $(c, a, g)$ is universalized, then 
if $p1$ believes that $p2$ believes they are in the given circumstances, then $p1$ believes 
that $p2$ performs the act. In other words, $p1$ will believe that 
$p2$ wills the maxim. I will refer to this as the ``convention of willing'' assumption. This follows

@@

wills it and thus notices the pattern of everyone willing it. If you observe that many do $X$ in circumstances $C$,
you will assume that everyone does $X$ in circumstance $C$.%

@@

and of ordinary definitions of lying. These thin assumptions were sufficient to recreate Korsgaard's solution
to an open ethical problem. Armed with this common sense, my system generated 

@@

While this example demonstrates the power of my system, it
also shows how vital the role of the common sense reasoning is. Slight, intuitive changes in the factual
background achieved completely different conclusions about lying. This example also demonstrates the importance
and difficulty of correctly formulating the maxim, particularly its circumstances.
Korsgaard's argument for the permissibility of lying to a 
murderer hinged on a clever formulation of the maxim that highlights the fact that the murderer is lying to you.
The need for common sense reasoning to evaluate the universalizability test and to formulate a maxim
is a potential limitation of my system, and I adress this concern in Section \ref{AIethics}.

@@

these kinds of judgements demonstrate that, with additional work, my system could be used in practice 
to guide AI agents. The idea of AI making decisions as in the dilemmas above may seem far-fetched, but
such scenarios are already becoming reality. For example, a ``smart doorbell'' may face a dilemma like that of
the murderer at the door. Such an AI agent equipped with a future version of my 

@@

%:%135=90%:%
%:%136=91%:%
%:%137=92%:%
%:%138=93%:%
%:%139=94%:%
%:%140=95%:%
%:%141=96%:%
%:%143=99%:%
%:%144=99%:%
%:%146=100%:%
%:%147=101%:%
%:%148=101%:%
%:%149=102%:%
%:%150=102%:%
%:%151=103%:%
%:%153=104%:%
%:%154=104%:%
%:%155=105%:%
%:%156=105%:%
%:%157=106%:%
%:%159=107%:%
%:%160=108%:%
%:%161=109%:%
%:%162=110%:%
%:%163=111%:%
%:%166=115%:%
%:%167=116%:%
%:%168=117%:%
%:%169=118%:%
%:%170=119%:%
%:%171=120%:%
%:%172=121%:%
%:%173=122%:%
%:%174=123%:%
%:%175=124%:%
%:%177=126%:%
%:%178=126%:%
%:%179=127%:%
%:%181=128%:%
%:%184=130%:%
%:%185=131%:%
%:%186=132%:%
%:%187=133%:%
%:%188=134%:%
%:%189=135%:%
%:%190=136%:%
%:%191=137%:%
%:%192=138%:%
%:%193=139%:%
%:%194=140%:%
%:%195=141%:%
%:%196=142%:%
%:%198=144%:%
%:%199=144%:%
%:%201=145%:%
%:%202=146%:%
%:%203=147%:%
%:%204=147%:%
%:%205=148%:%
%:%206=148%:%
%:%208=149%:%
%:%209=150%:%
%:%210=150%:%
%:%211=151%:%
%:%212=151%:%
%:%214=152%:%
%:%217=154%:%
%:%218=155%:%
%:%219=156%:%
%:%220=157%:%
%:%222=159%:%
%:%223=159%:%
%:%224=160%:%
%:%225=161%:%
%:%227=162%:%
%:%228=162%:%
%:%229=163%:%
%:%231=164%:%
%:%232=165%:%
%:%233=165%:%
%:%234=166%:%
%:%236=167%:%
%:%237=168%:%
%:%238=169%:%
%:%239=170%:%
%:%240=171%:%
%:%241=172%:%
%:%242=172%:%
%:%243=173%:%
%:%245=174%:%
%:%246=174%:%
%:%247=175%:%
%:%254=176%:%
%:%255=176%:%
%:%256=177%:%
%:%257=177%:%
%:%258=178%:%
%:%259=178%:%
%:%261=179%:%
%:%262=180%:%
%:%263=181%:%
%:%264=182%:%
%:%265=182%:%
%:%266=183%:%
%:%267=183%:%
%:%268=184%:%
%:%269=184%:%
%:%270=185%:%
%:%271=185%:%
%:%272=186%:%
%:%273=186%:%
%:%274=186%:%
%:%276=187%:%
%:%277=188%:%
%:%278=188%:%
%:%279=189%:%
%:%289=191%:%
%:%290=192%:%
%:%291=193%:%
%:%292=194%:%
%:%293=195%:%
%:%294=196%:%
%:%295=197%:%
%:%296=198%:%
%:%297=199%:%
%:%298=200%:%
%:%299=201%:%
%:%300=202%:%
%:%301=203%:%
%:%302=204%:%
%:%303=205%:%

@@

%:%306=207%:%
%:%307=208%:%
%:%309=209%:%
%:%310=210%:%
%:%313=212%:%
%:%314=213%:%
%:%315=214%:%
%:%316=215%:%
%:%317=216%:%
%:%318=217%:%
%:%319=218%:%
%:%320=219%:%
%:%321=220%:%

@@

%:%324=222%:%
%:%325=223%:%
%:%326=224%:%

@@

%:%329=225%:%
%:%330=226%:%
%:%332=227%:%

@@

%:%334=228%:%
%:%335=229%:%

@@

%:%338=230%:%
%:%339=231%:%

@@

%:%342=232%:%
%:%343=233%:%
%:%346=234%:%

@@

%:%351=234%:%
%:%353=235%:%
%:%354=236%:%
%:%355=237%:%
%:%356=238%:%
%:%357=239%:%
%:%367=242%:%
%:%368=243%:%
%:%369=244%:%
%:%370=245%:%
%:%371=246%:%
%:%372=247%:%
%:%373=248%:%
%:%374=249%:%
%:%375=250%:%
%:%376=251%:%
%:%377=252%:%
%:%378=253%:%
%:%379=254%:%
%:%380=255%:%
%:%381=256%:%
%:%382=257%:%
%:%383=258%:%
%:%384=259%:%
%:%385=260%:%
%:%386=261%:%
%:%387=262%:%
%:%388=263%:%
%:%389=264%:%
%:%390=265%:%
%:%391=266%:%
%:%392=267%:%
%:%393=268%:%
%:%394=269%:%
%:%395=270%:%
%:%396=271%:%
%:%397=272%:%
%:%398=273%:%
%:%399=274%:%
%:%400=275%:%
%:%401=276%:%
%:%402=277%:%
%:%403=278%:%
%:%404=279%:%
%:%405=280%:%
%:%406=281%:%
%:%407=282%:%
%:%408=283%:%
%:%409=284%:%
%:%410=285%:%
%:%411=286%:%
%:%420=289%:%
%:%432=292%:%
%:%433=293%:%
%:%434=294%:%
%:%435=295%:%
%:%436=296%:%
%:%437=297%:%
%:%438=298%:%
%:%439=299%:%
%:%440=300%:%
%:%441=301%:%
%:%442=302%:%
%:%443=303%:%
%:%444=304%:%
%:%445=305%:%
%:%446=306%:%
%:%447=307%:%
%:%448=308%:%
%:%449=309%:%
%:%450=310%:%
%:%452=312%:%

@@

@@

%:%457=314%:%

@@

%:%460=315%:%

@@

%:%464=318%:%

@@

@@

%:%469=320%:%

@@

@@

%:%475=322%:%

@@

%:%478=324%:%
%:%479=325%:%
%:%482=327%:%
%:%483=328%:%
%:%484=329%:%
%:%485=330%:%
%:%487=332%:%

@@

@@

%:%493=334%:%

@@

@@

%:%498=337%:%

@@

@@

%:%504=339%:%

@@

%:%507=341%:%
%:%508=342%:%
%:%524=374%:%
%:%525=375%:%
%:%526=376%:%
%:%527=377%:%
%:%528=378%:%
%:%529=379%:%
%:%530=380%:%
%:%531=381%:%
%:%532=382%:%

@@

%:%535=384%:%
%:%536=385%:%

@@

@@

%:%540=387%:%

@@

@@

%:%544=389%:%

@@

%:%547=391%:%
%:%548=392%:%
%:%549=393%:%

@@

%:%552=395%:%

@@

%:%555=397%:%
%:%556=398%:%
%:%557=399%:%
%:%558=400%:%
%:%559=401%:%

@@

%:%562=403%:%

@@

@@

%:%567=406%:%
%:%568=407%:%
%:%571=408%:%
%:%575=408%:%
%:%576=408%:%

@@

%:%579=409%:%
%:%580=410%:%
%:%581=411%:%
%:%591=413%:%
%:%592=414%:%
%:%593=415%:%
%:%594=416%:%

@@

%:%597=418%:%

@@

@@

%:%601=420%:%

@@

@@

%:%605=422%:%

@@

@@

%:%609=424%:%

@@

@@

%:%613=426%:%

@@

@@

%:%618=429%:%
%:%619=430%:%

@@

%:%630=433%:%

@@

%:%635=435%:%

@@

%:%640=437%:%

@@

%:%642=437%:%
%:%643=438%:%
%:%653=440%:%
%:%654=441%:%
%:%655=442%:%
%:%656=443%:%
%:%657=444%:%
%:%658=445%:%
%:%659=446%:%
%:%660=447%:%
%:%661=448%:%
%:%662=449%:%
%:%663=450%:%
%:%664=451%:%
%:%665=452%:%
%:%666=453%:%
%:%667=454%:%
%:%668=455%:%
%:%669=456%:%
%:%670=457%:%
%:%671=458%:%
%:%672=459%:%
%:%673=460%:%
%:%674=461%:%
%:%675=462%:%
%:%676=463%:%
%:%677=464%:%
%:%678=465%:%
%:%679=466%:%
%:%680=467%:%
%:%681=468%:%
%:%682=469%:%
%:%683=470%:%
%:%684=471%:%
%:%685=472%:%
%:%686=473%:%
%:%687=474%:%
%:%688=475%:%
